Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
remove portion of sentence about inter-rater repeatability in the literature
escape '>' characters in text

The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

@@

We acknowledge that the number of article that are cross-scored is low.
However, our aim was not to test inter-rater reproducibility, this is covered at length in the plant pathology literature.
Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.

@@

>>>>

The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (\> 0), 75.92% of being significant (\> 0.05), and 0.00% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).

@@

We acknowledge that the number of article that are cross-scored is low.
However, our aim was not to test inter-rater reproducibility.
Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.
Therefore, we concluded that the inter-rater agreement was good enough for this paper to illustrate that code and data are not being widely shared with peer-reviewed publications.

@@

## Closing
